---
title: "Iteration"
output: github_notebook
---

```{r setup}
library(tidyverse)
library(repurrrsive)
library(broom)
names(sw_people) <- sw_people %>% map_chr("name")

# Toy data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)

extra_credit <- list(0, 0, 10, 10, 15)

names(who) <- str_replace(names(who), "newrel", "new_rel")
tb <-  
  who %>%
  gather("codes", "n", 5:60) %>%
  separate(codes, c("new", "type", "sexage"), sep = "_") %>%
  select(-new, -iso2, -iso3) %>%
  separate(sexage, c("sex", "age"), sep = 1) %>%
  drop_na(n)
```

# Mapping

## purrr
```{r}
sw_people %>% pluck(11, "height")
```


## Your Turn 1

Run the code in the chunk. What does it do?

```{r}
#View(exams)
exams %>% map(median)
```

## map shorthand

```{r}
x<- c("hw1", "hw2", "hw3", "hw4", "hw5", "hw6", "hw7", "hw8", "hw9","hw10")
set_names(exams$student1, nm = x)
exams %>% map(set_names, nm =x) %>% 
  map_dfr(bind_rows) %>% 
summarise(across(hw1:hw10, mean))
```

## Your Turn 2

Complete the code to apply the test below to every element of the list. Return the results as a vector.

`length(<input>) == 10`

```{r}
exams %>% map_lgl(~length(.) == 10)
```

## Your Turn 3

Recompute the grades by dropping the lowest score and then taking the mean of the rest, i.e. Return the results as a _double_ vector.

`(sum(<input>) - min(<input>)) / 9`

```{r}
exams %>% map_dbl(~(sum(.) - min(.)) / 9)
```


## Your Turn 4

Compute a final grade for each student, where the final grade is the average test score plus any `extra_credit` assigned to the student. Return the results as a double (i.e. numeric) vector.

`mean(<exams>) + <extra_credit>`

```{r}
exams %>% 
  map2_dbl(extra_credit, ~mean(.x) + .y)
```


# Putting it all together

Predict TB cases in 2020 for Afghanistan

```{r}
tb %>% 
  filter(country == "Afghanistan") %>%
  group_by(year) %>% 
  summarise(n = sum(n)) %>%
  ggplot(aes(x = year, y = n)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```


```{r}
tb %>% 
  filter(country == "Afghanistan") %>%
  group_by(year) %>% 
  summarise(n = sum(n)) %>% 
  lm(n ~ year, data = .) %>% 
  predict(newdata = tibble(year = 2020)) %>% 
  round()
```

Predict TB cases in 2020 for each country

```{r}
tb_predictions <-
  tb %>% 
  group_by(country, year) %>% 
  summarise(n = sum(n)) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(n ~ year, data = .))) %>%
  mutate(pred = map_dbl(model, predict, tibble(year = 2020))) %>%
  mutate(pred = round(pred))

tb_predictions %>%  unnest(data, .drop = FALSE)
```

Things that we can now do:

* Which countries will have the most cases?
* What does the data look like for India?
* How do the Korea's compare?


```{r}
tb_predictions %>% 
  select(country, pred) %>% 
  arrange(desc(pred))
```

```{r}
tb_predictions %>%
  filter(country=="India") %>% 
  unnest(data)
```

```{r}
tb_predictions %>%
  filter(str_detect(country,"Korea")) %>% 
  select(country, pred) 
```


***

Take Aways

* Use `View()` to inspect lists
* Use `pluck()`, `[[ ]]`, or `$` to extract values from lists
* Use purrr's `map()` functions to manipulate lists
* Lists can be a column in a data frame
* Tables are an organizational structure that you can manipulate.
